Superabsorption of light by nanoparticles

### 2015-09-08 2015-Ladutenko-Qabs/submission-nanoscale/comm_template/response-letter/response-letter.tex

\vspace{10pt}

\textbf{Reviewer \#1 comments}

\begin{tabular}[!H]{l|p{0.9\textwidth}}
\quad & 1. The authors claimed “Combined effect of these resonances is presented to produce the flat and relative broadband electric resonance response.” Nevertheless, the broadened absorption band is not very broad. Is there any further way to predict a broadband light absorption. For instance, a broadband absorption in the whole visible spectral range. Maybe, a possible way of using the dispersed size scale nanoparticles should be added for improving the study. 
\end{tabular}

400-700 3-layer
4-layer?

В статье этого графика нет, есть обсуждение, готовим новую статью.

@@

In order to reply to this comment we run an optimization ... No changes
to the manuscript were made.

\begin{tabular}[!H]{l|p{0.9\textwidth}}
  \quad & 2. To achieve super-absorption behavior, it is interesting
  to know what will happen when the multilayered nanoparticles are
  closely packed as the plasmonic crystal. As reported in the previous
  papers [ACS Applied Materials \& Interfaces, 7, 4962−4968 (2015);
  Materials Letters 158, 262–265 (2015); Applied Physics Letters, 104,
  081116 (2014); Nanotechnology, 24, 155203 (2013)], the packed
  plasmonic crystals have been demonstrated to show broadband light
  coupling and confinement. Thereby, it would be interesting to show
  improved broadband light absorption based on the plasmonic crystal
  of this proposed multilayered nanoparticles. 
\end{tabular}

Lumerical - periodic boundary - попробовать несколько частиц

@@

It should be mentioned that .... No changes to the
manuscript were made.

\vspace{10pt}

\begin{minipage}{1.0\linewidth}
  \textbf{Reviewer \#2 comments}\\
  \begin{tabular}[!H]{l|p{0.9\textwidth}}
    \quad & 1.  As we can find from the manuscript, the highest
    absorption efficiency is achieved for a Si/Ag core-shell
    structure, which is not located in the super absorbing
    regime. Moreover, the authors also claimed that from practical
    aspect, the core-shell structure (not in the super absorbing
    regime) could be easier and cheaper to fabricate than three
    layered structure (in the super absorbing regime). Therefore, the
    authors should clearly clarify what are the advantages or
    significances of the super absorption nanoparticles? 
\end{tabular}
\end{minipage}

Для маленьких толщин лучше простой диполь, если есть ограничения на
минимальный размер частицы - лучше суперпоглотитель. Или, например,
если важно ещё и абсолютное поглощение от одиночной частицы - большая
частица поглощает больше, для неё оптимальнее работа в супер- режиме.

@@

There are several points to be treated carefully when discussing...
 However, to claim this concept to be a general one ...  more simulations
should be performed.

\begin{tabular}[!H]{l|p{0.9\textwidth}}
  \quad &  2.      In Fig. 2, we noticed a discontinuity at ~80
  nm. The authors explain it as the design supporting electric dipole
  and magnetic quadrupole has larger ACS. However, this explanation is
  not clearly to me since it is lacking physics behind this
  phenomenon. The authors should clarify why the magnetic quadrupole
  only plays a significant role in this small wavelength range. 
\end{tabular}

\begin{tabular}[!H]{l|p{0.9\textwidth}}
\quad & 3.      In Fig. 3 (c), the authors observed a flat top of
electric dipole resonance. They attributed this flat resonance to the
excited several electric dipole resonances with close resonance
frequencies. Nevertheless, as we can see in Fig. 3 (d), even without
considering the resonances located in outer and inner shell, the
resonance inside the core is much broader than the other two
cases. The authors should explain this broadened resonance clearly. 
\end{tabular}

Да, он прав, основной вклад от ядра, остальные делают верхушку
плоской. Фишка в том что резонанс плоский, а не широкий.

\begin{tabular}[!H]{l|p{0.9\textwidth}}
\quad & 4.      Some sentences are not clear to me. For instance,
“there is a strong conterplay between the increased absorption for
larger particles vs size for smaller particles”. 
In summary, I do not think the manuscript is acceptable at its current
stage. 
\end{tabular}

Илья

\\
\vspace{10pt}
\\
Sincerely Yours,\\
On behalf of the authors,\\
Konstantin Ladutenko
\end{document}

### 2015-09-11 2015-Ladutenko-Qabs/submission-nanoscale/comm_template/response-letter/response-letter.tex

\vspace{10pt}

\textbf{Reviewer \#1 comments}

\begin{tabular}[!H]{l|p{0.9\textwidth}}
\quad & 1. The authors claimed “Combined effect of these resonances is presented to produce the flat and relative broadband electric resonance response.” Nevertheless, the broadened absorption band is not very broad. Is there any further way to predict a broadband light absorption. For instance, a broadband absorption in the whole visible spectral range. Maybe, a possible way of using the dispersed size scale nanoparticles should be added for improving the study. 
\end{tabular}

This comment touches two aspects of broadband performance, namely,
properties of a stanalone particle and in interaction with other
particles.  The first case, as it was correctly mentioned with the
reviewer, has some limiations.  We can design a band, which will be
wider of a typical band for a given multipole, however, it`s width is
not extremly large.  To illustrate this we have run an optimization
with a goal to provide a prediefined separation between multipole
resonanses (Fig.~\ref{fig:broadband}).
\begin{figure}
  \begin{minipage}[h]{0.49\textwidth}    \begin{flushleft}     a)    \end{flushleft}
  \end{minipage}
  \begin{minipage}[h]{0.49\textwidth}    \begin{flushleft}     b)    \end{flushleft}
  \end{minipage}
  \begin{minipage}[h]{0.49\textwidth} 
   \includegraphics[width=0.95\textwidth]{band20-em}
  \end{minipage}
  \begin{minipage}[h]{0.49\textwidth} 
   \includegraphics[width=0.95\textwidth]{band20-em-ch}
  \end{minipage}
  \begin{minipage}[h]{0.49\textwidth}    \begin{flushleft}     c)    \end{flushleft}
  \end{minipage}
  \begin{minipage}[h]{0.49\textwidth}    \begin{flushleft}     d)    \end{flushleft}
  \end{minipage}
  \begin{minipage}[h]{0.49\textwidth} 
   \includegraphics[width=0.95\textwidth]{band80-em}
  \end{minipage}
  \begin{minipage}[h]{0.49\textwidth} 
    \includegraphics[width=0.95\textwidth]{band80-em-ch}
  \end{minipage}  
  \begin{minipage}[h]{0.49\textwidth}    \begin{flushleft}     e)    \end{flushleft}
  \end{minipage}
  \begin{minipage}[h]{0.49\textwidth}    \begin{flushleft}     f)    \end{flushleft}
  \end{minipage}
  \begin{minipage}[h]{0.49\textwidth} 
   \includegraphics[width=0.95\textwidth]{band80-e}
  \end{minipage}
  \begin{minipage}[h]{0.49\textwidth} 
    \includegraphics[width=0.95\textwidth]{band80-e-ch}
  \end{minipage}  
   \caption{Single particle desings for separation between dipole
     resonances of 20 nm (a-b) and 80 nm (c-f). Left column with
     figures (a,c,e) contains spectra of Mie efficiency for extinction
     (Qext), scattering (Qsca), absorption (Qabs, blue curve) and
     backscattering (Qbk). Right column (b,d,f) presents contibution
     of multipoles to the spectra (red and green stands for electric
     and magnetic dipoles, blue and cyan corresponds to quadrupole
     electric and magnetic modes, respectively). It is interesting to
     note that for 80 nm separation optimizer was able to find a
     desing with two resonances of a dipole mode (f). We suppose that
     the latter most likely has the same nature as the responce
     presented in Fig. 2(c,d) of the manuscript: there are several
     resonances of an electric dipole responce binded to different
     layers of the particle.\label{fig:broadband}}%
\end{figure}

Our observation is the following: while the separation is small enough
compared to a multiple resonance width the optimizer was successful to
find desings with electric and magnetic dipole. If the separation is
large the absorption band splits into two. For large separation is is
also possible to obtain two resonanses of the electric dipole
responce, located at predefined position
(Fig. \ref{fig:broadband}(e,f)).  Still there are not so many 
possibilities here to design a good wideband. To control the
bandwidth at a given spectral position we need to involeve relatively large particles. This
leads to appereance of resonances (and absorbtion) out of the designed band.

To answer the second part of the comment, related to possiblity of
usage of the pariticle array with dispered sizes, we designed two
particles with best absorption effeciency at 475~nm and 525~nm and
simulatied them both with FDTD method using Lumerical FDTD Solutions.
Sketch of the simulated system is in Fig.~\ref{fig:fdtd}

\begin{figure}
  \begin{minipage}[h]{0.49\textwidth}    \begin{flushleft}     a)    \end{flushleft}
  \end{minipage}
  \begin{minipage}[h]{0.49\textwidth}    \begin{flushleft}     b)    \end{flushleft}
  \end{minipage}
  \begin{minipage}[h]{0.49\textwidth} 
   \includegraphics[width=0.95\textwidth]{FDTD-mode-d00}
  \end{minipage}
  \begin{minipage}[h]{0.49\textwidth} 
   \includegraphics[width=0.95\textwidth]{fdtd-spectra}
  \end{minipage}
   \caption{.\label{fig:fdtd}}%
\end{figure}

% band80-e
% Si-Ag-Si-TotalR058.00nm-Qabs02.4351291413952--core0013.16nm--inshell0041.41nm--outshell0003.43nm-fails0-spectra
% band80-em
% Si-Ag-Si-TotalR064.00nm-Qabs02.6266428870829--core0024.22nm--inshell0024.50nm--outshell0015.28nm-fails0-spectra
% band20-e
% Si-Ag-Si-TotalR058.00nm-Qabs03.9125128013731--core0010.44nm--inshell0042.75nm--outshell0004.81nm-fails0-spectra
% band20-em
% Si-Ag-Si-TotalR062.00nm-Qabs05.0835852277006--core0028.20nm--inshell0011.88nm--outshell0021.91nm-fails0-spectra

%% 400-700 3-layer
%% 4-layer?

%% В статье этого графика нет, есть обсуждение, готовим новую статью.

%% In order to reply to this comment we run an optimization ...

We changed the manuscript ``The stochastic algorithm utilized in our approach is very
generic and the optimization can be repeated for any desired
wavelength or wavelength range. As a result, one can design
spectrally-selective absorbers or broadband absorbers with almost
arbitrary prescribed properties.''

@@

\begin{tabular}[!H]{l|p{0.9\textwidth}}
  \quad & 2. To achieve super-absorption behavior, it is interesting
  to know what will happen when the multilayered nanoparticles are
  closely packed as the plasmonic crystal. As reported in the previous
  papers [ACS Applied Materials \& Interfaces, 7, 4962−4968 (2015);
  Materials Letters 158, 262–265 (2015); Applied Physics Letters, 104,
  081116 (2014); Nanotechnology, 24, 155203 (2013)], the packed
  plasmonic crystals have been demonstrated to show broadband light
  coupling and confinement. Thereby, it would be interesting to show
  improved broadband light absorption based on the plasmonic crystal
  of this proposed multilayered nanoparticles. 
\end{tabular}

%% Lumerical - periodic boundary - попробовать несколько частиц

@@

We totally agree with the reviewer's statement. It seems that our
manuscript was not clear enough at this point. ...  However, as we
compare final optimization results we conclude that .... To make it
clearer we rewrite this part of the manuscript as follows:

\begin{tabular}[!H]{p{0.9\textwidth}}
`` Some text''
\end{tabular}

%% It should be mentioned that .... No changes to the
%% manuscript were made.

@@

\vspace{10pt}

\begin{minipage}{1.0\linewidth}
  \textbf{Reviewer \#2 comments}\\
  \begin{tabular}[!H]{l|p{0.9\textwidth}}
    \quad & 1.  As we can find from the manuscript, the highest
    absorption efficiency is achieved for a Si/Ag core-shell
    structure, which is not located in the super absorbing
    regime. Moreover, the authors also claimed that from practical
    aspect, the core-shell structure (not in the super absorbing
    regime) could be easier and cheaper to fabricate than three
    layered structure (in the super absorbing regime). Therefore, the
    authors should clearly clarify what are the advantages or
    significances of the super absorption nanoparticles? 
\end{tabular}
\end{minipage}

%% Для маленьких толщин лучше простой диполь, если есть ограничения на
%% минимальный размер частицы - лучше суперпоглотитель. Или, например,
%% если важно ещё и абсолютное поглощение от одиночной частицы - большая
%% частица поглощает больше, для неё оптимальнее работа в супер- режиме.

%% There are several points to be treated carefully when discussing...
%%  However, to claim this concept to be a general one ...  more simulations
%% should be performed.

@@

\begin{tabular}[!H]{l|p{0.9\textwidth}}
  \quad &  2.      In Fig. 2, we noticed a discontinuity at ~80
  nm. The authors explain it as the design supporting electric dipole
  and magnetic quadrupole has larger ACS. However, this explanation is
  not clearly to me since it is lacking physics behind this
  phenomenon. The authors should clarify why the magnetic quadrupole
  only plays a significant role in this small wavelength range. 
\end{tabular}

\begin{tabular}[!H]{l|p{0.9\textwidth}}
\quad & 3.      In Fig. 3 (c), the authors observed a flat top of
electric dipole resonance. They attributed this flat resonance to the
excited several electric dipole resonances with close resonance
frequencies. Nevertheless, as we can see in Fig. 3 (d), even without
considering the resonances located in outer and inner shell, the
resonance inside the core is much broader than the other two
cases. The authors should explain this broadened resonance clearly. 
\end{tabular}

%% Да, он прав, основной вклад от ядра, остальные делают верхушку
%% плоской. Фишка в том что резонанс плоский, а не широкий.

\begin{tabular}[!H]{l|p{0.9\textwidth}}
\quad & 4.      Some sentences are not clear to me. For instance,
“there is a strong conterplay between the increased absorption for
larger particles vs size for smaller particles”. 
In summary, I do not think the manuscript is acceptable at its current
stage. 
\end{tabular}%
%% Илья
\\
\vspace{10pt}
\\
Sincerely Yours,\\
On behalf of the authors,\\
Konstantin Ladutenko
\end{document}

### 2015-09-16 2015-Ladutenko-Qabs/submission-nanoscale/comm_template/response-letter/response-letter.tex

I would like to thank the editor and two anonymous reviewers for their
constructive comments, which helped us to improve the
manuscript. Below, we address all comments point-by-point, discussing
the subsequent modifications.

\vspace{10pt}

\textbf{Reviewer \#1 comments}

\begin{tabular}[!H]{l|p{0.9\textwidth}}
\quad & 1. The authors claimed “Combined effect of these resonances is presented to produce the flat and relative broadband electric resonance response.” Nevertheless, the broadened absorption band is not very broad. Is there any further way to predict a broadband light absorption. For instance, a broadband absorption in the whole visible spectral range. Maybe, a possible way of using the dispersed size scale nanoparticles should be added for improving the study. 
\end{tabular}\\

This comment touches two aspects of broadband performance, namely,
properties of a stanalone particle and in interaction with other
particles.  The first case, as it was correctly mentioned with the
reviewer, has some limiations.  We can design a band, which will be
broader of a typical band for a given multipole, however, it`s width is
not extremly large.  To illustrate this we have run an optimization
with a goal to provide a prediefined separation between multipole
resonanses (Fig.~\ref{fig:broadband}).
\begin{figure}
  \begin{minipage}[h]{0.49\textwidth}    \begin{flushleft}     a)    \end{flushleft}
  \end{minipage}
  \begin{minipage}[h]{0.49\textwidth}    \begin{flushleft}     b)    \end{flushleft}
  \end{minipage}
  \begin{minipage}[h]{0.49\textwidth} 
   \includegraphics[width=0.95\textwidth]{band20-em}
  \end{minipage}
  \begin{minipage}[h]{0.49\textwidth} 
   \includegraphics[width=0.95\textwidth]{band20-em-ch}
  \end{minipage}
  \begin{minipage}[h]{0.49\textwidth}    \begin{flushleft}     c)    \end{flushleft}
  \end{minipage}
  \begin{minipage}[h]{0.49\textwidth}    \begin{flushleft}     d)    \end{flushleft}
  \end{minipage}
  \begin{minipage}[h]{0.49\textwidth} 
   \includegraphics[width=0.95\textwidth]{band80-em}
  \end{minipage}
  \begin{minipage}[h]{0.49\textwidth} 
    \includegraphics[width=0.95\textwidth]{band80-em-ch}
  \end{minipage}  
  \begin{minipage}[h]{0.49\textwidth}    \begin{flushleft}     e)    \end{flushleft}
  \end{minipage}
  \begin{minipage}[h]{0.49\textwidth}    \begin{flushleft}     f)    \end{flushleft}
  \end{minipage}
  \begin{minipage}[h]{0.49\textwidth} 
   \includegraphics[width=0.95\textwidth]{band80-e}
  \end{minipage}
  \begin{minipage}[h]{0.49\textwidth} 
    \includegraphics[width=0.95\textwidth]{band80-e-ch}
  \end{minipage}  
   \caption{Single particle desings for separation between dipole
     resonances of 20 nm (a-b) and 80 nm (c-f). Left column with
     figures (a,c,e) contains spectra of Mie efficiency for extinction
     (Qext), scattering (Qsca), absorption (Qabs, blue curve) and
     backscattering (Qbk). Right column (b,d,f) presents contibution
     of multipoles to the spectra (red and green stands for electric
     and magnetic dipoles, blue and cyan corresponds to quadrupole
     electric and magnetic modes, respectively). It is interesting to
     note that for 80 nm separation optimizer was able to find a
     desing with two resonances of a dipole mode (f). We suppose that
     the latter most likely has the same nature as the responce
     presented in Fig. 3(c,d) of the manuscript: there are several
     resonances of an electric dipole responce binded to different
     layers of the particle.\label{fig:broadband}}%
\end{figure}
Our observation is the following: while the separation is small enough
compared to a multiple resonance width the optimizer was successful to
find desings with electric and magnetic dipole. If the separation is
large the absorption band splits into two. For large separation is is
also possible to obtain two resonanses of the electric dipole
responce, located at predefined position
(Fig. \ref{fig:broadband}(e,f)).  Still there are not so many
possibilities here to design a good broadband. To control the
bandwidth at a given spectral position we need to involeve relatively
large particles. This leads to appereance of resonances (and
absorbtion) out of the designed band which are hard to control or
suppress in disscussed triple-layer structure.

To answer the second part of the comment, related to possiblity of
usage of the pariticle array with dispered sizes, we designed two
particles with best absorption effeciency at 475~nm and 525~nm and
simulatied them both with FDTD method using Lumerical FDTD Solutions.
Sketch of the simulated system and final results are in
Fig.~\ref{fig:fdtd}. To verify our FDTD we fist simulated absorption
of standalone spheres, the obtained postions and amplitudes of
resonances corresponde well with Mie caclulations.
\begin{figure}
  \begin{minipage}[h]{0.49\textwidth}    \begin{flushleft}     a)    \end{flushleft}
  \end{minipage}
  \begin{minipage}[h]{0.49\textwidth}    \begin{flushleft}     b)    \end{flushleft}
  \end{minipage}
  \begin{minipage}[h]{0.49\textwidth} 
   \includegraphics[width=0.95\textwidth]{FDTD-mode-d00}
  \end{minipage}
  \begin{minipage}[h]{0.49\textwidth} 
   \includegraphics[width=0.95\textwidth]{fdtd-spectra}
  \end{minipage}
   \caption{(a) Fullwave simulation prepared in Lumerical FDTD. (b)
     Absorption spectra of stand-alone spheres and in dimer
     configuration with separation between spheres of 0, 10, and 30~nm.\label{fig:fdtd}}%
\end{figure}
Next step was to find out the possible interactions between two
spheres, so we run a simulation in dimer configuration with zero
separation between spheres and with 10 and 30~nm separation.  The
resulting spectra has a strong contribution from standalone
resonances, while coupling effects seems to be minor.  This can be
easily explained from field distribution in Fig.~4(c) of the
manuscript. Positioning spheres in H-k plane we are exploting the
feature of field being highly localized inside the the sphere.  For
sure arranging spheres in other plane, increasing the number of
spheres can change the amount of coupling between the spheres. Still,
here we show that in principle it is possible to construct an
absoption band of an array of dispersed particles simply optimizing
the properties of every single sphere.

We changed the manuscript from ``As a result, one can design
spectrally-selective absorbers or broadband absorbers with almost
arbitrary prescribed properties.'' to ``As a result, one can design
absorbers with broadened spectra or spectrally-selective absorbers
with almost arbitrary prescribed properties.  Due to high localization
of field inside the particle (espatially in H-k plane) it is also
possible to desing arrays of dispersed size particles by defining the
properties of individual particles; we obtained rather small coupling
between particles during additional simulation using FDTD method.''

### 2015-09-17 2015-Ladutenko-Qabs/submission-nanoscale/comm_template/response-letter/response-letter.tex

To answer the second part of the comment, related to possiblity of
usage of the pariticle array with dispered sizes, we designed two
particles with best absorption effeciency at 475~nm and 525~nm (outer
radius 34 and 38~nm) and
simulatied them both with FDTD method using Lumerical FDTD Solutions.
Sketch of the simulated system and final results are in
Fig.~\ref{fig:fdtd}. To verify our FDTD we fist simulated absorption
of standalone spheres, the obtained postions and amplitudes of
resonances corresponde well with Mie caclulations.
\begin{figure}
  \begin{minipage}[h]{0.49\textwidth}    \begin{flushleft}     a)    \end{flushleft}
  \end{minipage}
  \begin{minipage}[h]{0.49\textwidth}    \begin{flushleft}     b)    \end{flushleft}
  \end{minipage}
  \begin{minipage}[h]{0.49\textwidth} 
   \includegraphics[width=0.95\textwidth]{FDTD-mode-d00}
  \end{minipage}
  \begin{minipage}[h]{0.49\textwidth} 
   \includegraphics[width=0.95\textwidth]{fdtd-spectra}
  \end{minipage}
  \begin{minipage}[h]{0.49\textwidth}    \begin{flushleft}     c)    \end{flushleft}
  \end{minipage}
  \begin{minipage}[h]{0.49\textwidth}    \begin{flushleft}     d)   \end{flushleft}
  \end{minipage}
  \begin{minipage}[h]{0.49\textwidth} 
    \includegraphics[width=0.95\textwidth]{fdtd-spectra-Ek}
  \end{minipage}
  \begin{minipage}[h]{0.49\textwidth} 
    \includegraphics[width=0.95\textwidth]{fdtd-field}
  \end{minipage}
    \caption{(a) Fullwave simulation prepared in Lumerical FDTD. (b)
     Absorption spectra of stand-alone spheres and in dimer
     configuration with separation between spheres of 0, 10, and
     30~nm, particles are in H-k plane (c) Separation 0 and 30~nm for
     particles in E-k plane (d) Field distribution at 500nm of
     incedent wavelength for particles in E-k plane with separation of
     30~nm.\label{fig:fdtd}}%
\end{figure}
Next step was to find out the possible interactions between two
spheres, so we run a simulation in dimer configuration with zero
separation between spheres and with 10 and 30~nm separation.  The
resulting spectra has a strong contribution from standalone
resonances, while coupling effects seems to be minor.  This can be
easily explained from field distribution in Fig.~4(c) of the
manuscript. Positioning spheres in H-k plane we are exploting the
feature of field being highly localized inside the the sphere.  For
sure arranging spheres in other plane, increasing the number of
spheres can change the amount of coupling between the spheres. Still,
here we show that in principle it is possible to construct an
absoption band of an array of dispersed particles simply optimizing
the properties of every single sphere.

### 2015-09-24 2015-Ladutenko-Qabs/submission-nanoscale/comm_template/2015-Ladutenko-Qabs.tex
Proposed changed to the manuscipt are now in the responce letter

\begin{figure}[h]
  \center{
    % Use pdfcrop to remove white margins
    \includegraphics[width=0.45\textwidth]{2015-04-01-SiAgSi-ab-spectra4}%
    \caption{Spectra of Mie absorption coefficients of (a) efficient and (b-c)superabsorption design. Panel (d) shows the superposition of the squared absolute values of the Mie coefficients for electric dipole contribution inside each layer. 
      \label{fig:spectra}
    }%
  }
\end{figure}
To study spectral properties of structures with large ACS which we
obtained by the optimization, in Fig.~\ref{fig:spectra} we plot three
different cases for designs that correspond to local maxima of $Q_{\rm
  abs}$ shown in Fig.~\ref{fig:overview}~(a).  As expected, the design
corresponding to the maximum absorption efficiency at $R=36$~nm has a
single electric dipole resonance centered at the target wavelength
$\lambda=500$~nm. Spectra of designs with maxima at $R=63$~nm and
$R=81$~nm have a signature of the superabsorption, i.e. there is an
overlap of several resonances.  We note that these structures have
additional absorption resonances, but they are located far from the
wavelength of interest.  A noticeable feature of
Fig.~\ref{fig:spectra}~(c) is an almost flat top of the electric
dipole resonance. More detailed analysis shows that we have {\em
  excited several electric dipole resonances} with close resonance
frequencies within our multilayer structure. Indeed, if we plot a
superposition of the squares of the absolute values of the Mie
coefficients, which characterize electric energy density stored in
each layer, we find that we excite resonances in all three layers, and
they are slightly offset as shown in
Fig.~\ref{fig:spectra}~(d). Combined effect of these resonances
produces the flat and relatively broadband electric resonance response
shown in Fig.~\ref{fig:spectra}~(c).

>>>>

\begin{figure}[h]
  \center{
    % Use pdfcrop to remove white margins
    \includegraphics[width=0.45\textwidth]{2015-04-01-SiAgSi-ab-spectra4}%
    \caption{Spectra of Mie absorption coefficients of (a)~efficient
      and (b-c)~superabsorption design. Panel~(d) shows the
      superposition of the squared absolute values of the Mie
      coefficients for electric dipole contribution inside each layer.
      \label{fig:spectra}
    }%
  }
\end{figure}
To study spectral properties of structures with large ACS which we
obtained by the optimization, in Fig.~\ref{fig:spectra} we plot three
different cases for designs that correspond to local maxima of $Q_{\rm
  abs}$ shown in Fig.~\ref{fig:overview}~(a).  As expected, the design
corresponding to the maximum absorption efficiency at $R=36$~nm has a
single electric dipole resonance centered at the target wavelength
$\lambda=500$~nm. Spectra of designs with maxima at $R=63$~nm and
$R=81$~nm have a signature of the superabsorption, i.e. there is an
overlap of several resonances.  We note that these structures have
additional absorption resonances, but they are located far from the
wavelength of interest.  A noticeable feature of
Fig.~\ref{fig:spectra}~(c) is an almost flat top of the electric
dipole resonance. More detailed analysis shows that we have {\em
  excited several electric dipole resonances} with close resonance
frequencies within our multilayer structure. Indeed, if we plot a
superposition of the squares of the absolute values of the Mie
coefficients, which characterize electric energy density stored in
each layer, we find that we excite resonances in all three layers, and
they are slightly offset as shown in
Fig.~\ref{fig:spectra}~(d). Combined effect of these resonances
produces the flat and relatively broadband electric resonance response
shown in Fig.~\ref{fig:spectra}~(c).
